\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% Font options
% \usepackage[sfdefault]{roboto}  % Roboto font
% \usepackage[default]{lato}    % Lato font
\usepackage[default]{sourcesanspro}    % Source Sans Pro
\usepackage{amssymb}
\usepackage{fontawesome5}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.6in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{\tiny$\blacktriangleright$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[itemsep=1pt, parsep=0pt, leftmargin=0.12in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADER----------
\begin{center}
    \textbf{\Huge \scshape Deepanshu Verma} \\ \vspace{5pt}
    \large Gen AI Engineer $|$ System Architect $|$ CTO \\ \vspace{5pt}
    \small \faPhone\ +91 7987170923 $|$ \href{mailto:deepanshu.verma@zohomail.in}{\underline{\faEnvelope\ deepanshu.verma@zohomail.in}} $|$ \href{https://www.linkedin.com/in/deepanshu-verma/}{\underline{\faLinkedin\ LinkedIn}} $|$ \href{https://github.com/Deepanshu-Verma-Work}{\underline{\faGithub\ GitHub}} $|$ \href{https://deepanshu-verma-work.github.io/deepanshu-portfolio/}{\underline{\faGlobe\ Portfolio}}
\end{center}


%-----------CAREER SUMMARY-----------
\section{Career Summary}
  \small{System Architect bridging the gap between 'Proof of Concept' and 'Enterprise Production'. Expert in designing secure, scalable, and cost-efficient cloud-native systems. Specializes in leveraging Serverless architectures and Generative AI to solve complex business problems with rapid time-to-market.}


%-----------EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Generative AI Engineer \& System Architect}{June 2025 -- Present}
      {CloudAge Global Services Pvt Ltd $|$ Pune}{}
      \resumeItemListStart
        \resumeItem{Architected serverless GenAI solutions on AWS (Bedrock, SageMaker), reducing latency and optimizing costs.}
        \resumeItem{Designed secure enterprise systems using VPCs, Private Subnets, and IAM Least Privilege principles.}
        \resumeItem{Implemented high-precision RAG systems and automated LLMOps evaluation workflows.}
        \resumeItem{Led strategic "Buy vs. Build" decisions to accelerate delivery and maximize ROI.}
      \resumeItemListEnd

    \resumeSubheading
      {Senior System Engineer}{June 2021 -- May 2025}
      {Duck Creek Technologies $|$ Pune, Maharashtra}{}
      \resumeItemListStart
        \resumeItem{Engineered scalable cloud infrastructure and data pipelines.}
        \resumeItem{Implemented robust CI/CD pipelines for automated deployments.}
        \resumeItem{Optimized system performance and reliability for enterprise-grade applications.}
        \resumeItem{Collaborated with cross-functional teams to deliver high-impact technical solutions.}
      \resumeItemListEnd

    \resumeSubheading
      {Hadoop Administrator \& Big Data Specialist}{2019 -- 2022}
      {Positive Edge Solution Pvt Ltd $|$ Pune}{}
      \resumeItemListStart
        \resumeItem{Managed and optimized enterprise-level Hadoop clusters (CDH), ensuring High Availability and robust fault tolerance.}
        \resumeItem{Engineered scalable data pipelines using AWS (S3, Glue) and Azure (ADF, Databricks), facilitating seamless cross-cloud data integration.}
        \resumeItem{Led the migration of on-premise legacy data systems to cloud-native architectures, reducing infrastructure costs and improving scalability.}
        \resumeItem{Implemented automated monitoring and performance tuning for Big Data infrastructure, significantly reducing downtime.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Heimdall (SafeZone AI) - Industrial Safety Monitoring} $|$ \emph{AWS Lambda, Rekognition, React, DynamoDB}}{}
          \resumeItemListStart
            \resumeItem{Architected a \textbf{Serverless, Event-Driven} solution for real-time PPE/Helmet detection, reducing TCO by $\sim$60\% compared to EC2.}
            \resumeItem{Integrated \textbf{Amazon Rekognition} for high-confidence (99\% availability) safety compliance monitoring without human spotters.}
            \resumeItem{Secured backend logic in a \textbf{Private VPC} with Interface Endpoints, ensuring no public internet exposure.}
            \resumeItem{Optimized \textbf{DynamoDB} access patterns, achieving <200ms latency for log retrieval.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{LexGuard - Legal Tech Platform} $|$ \emph{AWS Bedrock (Titan), Serverless, React}}{}
          \resumeItemListStart
            \resumeItem{Developed a serverless contract review platform using \textbf{Amazon Bedrock (Titan)} to automate legal risk analysis.}
            \resumeItem{Implemented secure document processing pipelines to handle sensitive legal data.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd





%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {NASSCOM}{2023 -- 2024}
      {PGDM in AI \& ML Ops}{}
    \resumeSubheading
      {Pune University}{Maharashtra}
      {Bachelors of Computer Engineering}{2016 -- 2020}
  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \begin{tabularx}{\linewidth}{ @{} l @{\hspace{1ex}} X @{} }
      \textbf{Cloud Architecture} & : AWS (Lambda, DynamoDB, API Gateway, SNS, S3, Cognito, VPC, IAM), Terraform, Serverless \\
      \textbf{Generative AI} & : Amazon Bedrock, Titan, Rekognition, Prompt Engineering, RAG \\
      \textbf{Development Stack} & : React, TypeScript, Node.js, Python, PostgreSQL \\
      \textbf{Core Competencies} & : System Design, Enterprise Security, Cost Optimization, CI/CD
     \end{tabularx}
    }}
 \end{itemize}



\end{document}
